---
title: "Chinese Loan and its Implication"
author: "Sisir Bhandari"
date: "2023-04-04"
output: ioslides_presentation
---

```{r setup1, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
```

```{r setup2, include=FALSE}
library(tidyverse)
library(pacman)
library(readxl)
library(ggplot2)
library(gridExtra)
library(scales)
```

```{r setup3, include=FALSE}
china<- read_excel("~/Desktop/American University /second/Data Analysis/Assignments/Assignment 5/China_Inv.xlsx")
```

## Chinese Overseas Loan
- Chinese International Financial Investments and Loan
- Two Policy Banks 
  (Chinese Development Bank and Export Import Bank)
- Time Series Data
  2008 to 2021
- South Asian Countries Overview
- Sri Lanka and Pakistan as a Case
- Implications
- Sources: Boston University, Global China Initiative
https://www.bu.edu/gdp/research/gci/
IMF and The World Bank


```{r setup4, include=FALSE}
#Subsetting
#CDB and CHEXIM Investments in Asia
asia <- subset(china, 
    china$COUNTRIES %in% c("Bangladesh") | 
(row.names(china) >= 156 & row.names(china) <= 177)|
      china$COUNTRIES %in% c("Maldives") | 
(row.names(china) >= 936 & row.names(china) <= 942) |
china$COUNTRIES %in% c("Nepal") | 
(row.names(china) >= 1029 & row.names(china) <= 1034) |
china$COUNTRIES %in% c("Sri Lanka") | 
(row.names(china) >= 1231 & row.names(china) <= 1285) |
  china$COUNTRIES %in% c("Pakistan") | 
(row.names(china) >= 1072 & row.names(china) <= 1107))
```

```{r setup5, include=FALSE}
asia <- asia[-c(1:13), ]
asia$AMOUNT <- as.numeric(gsub("[\\$M]", "", asia$AMOUNT))
```

```{r setup6, include=FALSE}
# Before Bangladesh and other countries
start_row <- which(asia$COUNTRIES == "Bangladesh")[1]
end_row <- min(which(asia$COUNTRIES %in% c("Maldives"))) - 1
bng <- asia[start_row:end_row, ]
colnames(bng)[1] <- "Bangladesh"
bng <- slice(bng, -1)
```

```{r setup7, include=FALSE}
start_row <- which(asia$COUNTRIES == "Maldives")[1]
end_row <- min(which(asia$COUNTRIES %in% c("Nepal"))) - 1
mal <- asia[start_row:end_row, ]
colnames(mal)[1] <- "Maldives"
mal <- slice(mal, -1)
```

```{r setup8, include=FALSE}
start_row <- which(asia$COUNTRIES == "Nepal")[1]
end_row <- min(which(asia$COUNTRIES %in% c("Pakistan"))) - 1
nep <- asia[start_row:end_row, ]
colnames(nep)[1] <- "Nepal"
nep <- slice(nep, -1)
```

```{r setup9, include=FALSE}
start_row <- which(asia$COUNTRIES == "Pakistan")[1]
end_row <- min(which(asia$COUNTRIES %in% c("Sri Lanka"))) - 1
pak <- asia[start_row:end_row, ]
colnames(pak)[1] <- "Pakistan"
pak <- slice(pak, -1)
```

```{r setup01, include=FALSE}
start_row <- which(asia$COUNTRIES == "Sri Lanka")[1]
end_row <- nrow(asia)
sln <- asia[start_row:end_row, ]
colnames(sln)[1] <- "Sri Lanka"
sln <- slice(sln, -1)
```

## Chinese Investment in Five South Asian Countries
```{r setup02, include=TRUE}
chexim <- subset(asia, LENDER == 'CHEXIM')
cdb <- subset(asia, LENDER == 'CDB')
```

```{r setup03, include=TRUE}
chexim <- filter(asia, LENDER == 'CHEXIM')
cdb<- filter(asia, LENDER == 'CDB')
```

```{r setup04, include=TRUE}
#total
tchexim<- sum(chexim$AMOUNT)
tcdb <- sum(cdb$AMOUNT)
tinv <- data.frame(
  LENDER = c("CHEXIM", "CDB"),
  tinve = c(tchexim, tcdb)
)
ggplot(tinv, aes(x=LENDER, y=tinve)) +
  geom_bar(stat="identity", fill="#AE4371") +
  labs(title="CDB and CHEXIM Investments - South Asia", x="Lender", y="Total Investment") +
  theme(plot.background = element_rect(fill = "#E8F8F5"),
axis.title = element_text(face = "bold"))
```



```{r setup05, include=FALSE}
ta <-sum(sln$AMOUNT)
#12,283
```


```{r setup06, include=FALSE}
t1 <-sum(mal$AMOUNT)
#951
```

```{r setup07, include=FALSE}
na.omit(bng)
t2 <-sum(bng$AMOUNT)
#15452
```

```{r setup08, include=FALSE}
na.omit(nep)
t3 <-sum(nep$AMOUNT)
#366
```


```{r setup09, include=FALSE}
t4 <-sum(pak$AMOUNT)
#22,635
```

## Country cases


```{r setup21, include=TRUE}
cf <- data.frame(
  Country = c("Sri Lanka", "Pakistan", "Nepal", "Bangladesh", "Maldives"),
  Loan = c(12283, 22635, 366, 15452, 951)
)
ggplot(cf, aes(x = Country, y = Loan, fill = Country)) +
  geom_point(shape = 21, color = "black", size = 4, alpha = 0.7) +
  scale_fill_manual(values = c("Sri Lanka" = "red", "Pakistan" = "blue", "Nepal" = "green", "Bangladesh" = "orange", "Maldives" = "purple")) +
  labs(title = "Loan by Country", x = "", y = "Amount") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 5),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10),
    plot.background = element_rect(fill = "#E8F8F5"),
    panel.background = element_rect(fill = "white")
  ) +
  coord_cartesian(ylim = c(0, 25000)) +
  guides(fill = guide_legend(title = "Country", ncol = 5))
```


## Taking Pakistan and Sri Lanka as a case

```{r setup20, include=FALSE}
five<- read_excel("~/Desktop/American University /second/Data Analysis/Assignments/Assignment 5/FIVE.xlsx")
```


```{r setup31, include=TRUE}
ggplot(five, aes(x = year, y = investment, color = country)) +
  geom_line(size = 1, na.rm = TRUE) +
  scale_color_manual(values = c("Pakistan" = "blue", "Sri Lanka" = "red")) +
  labs(title = "Chinese Investment over Time", x = "Year", y = "Investment (millions USD)") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 5),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10),
    plot.background = element_rect(fill = "#E8F8F5"),
    panel.background = element_rect(fill = "white")
  )
                

```

## Pakistan and Sri Lanka External Debt

```{r setup=33, include=FALSE}
seven<- read_excel("~/Desktop/American University /second/Data Analysis/Assignments/Assignment 5/seven.xlsx")
```


```{r setup46, include=TRUE}
seven$Debt <- seven$Debt/1000000000
```

```{r setup=35, include=TRUE}
ggplot(seven, aes(x = Year, y = Debt, color = Country)) +
  geom_line(size = 1) +
  scale_color_manual(values = c("Pakistan" = "blue", "Sri Lanka" = "red")) +
  labs(title = "Sri Lanka and Pakistan Debt", x = "Year", y = "Billions USD") +
  scale_y_continuous(labels = comma) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 5),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 10),
    plot.background = element_rect(fill = "#E8F8F5"),
    panel.background = element_rect(fill = "white")
  )
```

## Economic and Sovereign Debt Crisis
- Risky loans with higher interest rates
- Structural Adjustment Policies Overlook
- Lack of good governance and high corruption
- Geopolitics pawn

## Sources
- Boston University, Global China Initiative
- International Monetary Fund, Article IV Report
- The World Bank


